---
name: Efe
surname: Gülkan
position: "Student"
address: "Kartal - İstanbul"
phone: +90 (545) 326 0872
www: 
email: "efe.gulkan@outlook.com"
github: pimaniye41
linkedin: efegulkan
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::markdowncv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Summary

 * Ambitious 2nd year economics student who is willing to learn data science and work in data analysis field after graduation. Primary **R** language user with my analysis. Goal-oriented and practical approaches to projects. Plan to increase my knowledge in the field by internships and courses.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Courses,
  "Economics", "2020-", "Bahcesehir University", "Istanbul, Türkiye", "Introduction to Economics I-II, Data Science with R, Statistics for Economics I-II"
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Courses)
```

# Projects

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2022, "Sectoral Analysis", "Compared 400 BIST TUM firms' and 16 sectors' change in employee numbers and financials over 7 years in **R language**. - Completed",
  2022, "Getting data from CBTR EVDS to R using API", "Used API to import xml data to R, then converting it to data frame. - Completed",
  2022, "Employment and Election Analysis", "Comparing public employment and election results of provinces of Türkiye in **R language** - Ongoing",
  2023,"Web App", "Implementing basic statistical distributions into a **Shiny** web app - Ongoing",
  2023, "Web App","Implementing my Sectoral Analysis project into a web app with simple user interface on **Shiny** to filter years and sectors - Ongoing"
  
) %>% 
  detailed_entries(what = Type, when=Year, why= Desc
  )
```
## Links

* [Sectoral Analysis of BIST TUM firms and sectors](https://github.com/pimaniye41/R4DS_final_final)
* [Getting Data from CBRT EVDS](https://github.com/pimaniye41/evds_data)
* [Employment and Election Analysis](https://github.com/pimaniye41/employment_election)
* [Statistical Distributions Web App](https://github.com/pimaniye41/sample_calc)


## Certificates and Courses
* [What is Data Science by IBM Skills Network](https://www.coursera.org/account/accomplishments/verify/997HSSDB567B)
* [2nd Annual Bilkent Computational Social Sciences Summit Day 1 by Bilkent Social Sciences Society](https://bilkent-university-social-scie.verified.cv/en/verify/74268007028910) 
* [2nd Annual Bilkent Computational Social Sciences Summit Day 2 by Bilkent Social Sciences Society](https://bilkent-university-social-scie.verified.cv/en/verify/80720640647565)
* [Tools for Data Science by IBM Skills Network, ongoing](https://www.coursera.org/learn/open-source-tools-for-data-science?specialization=ibm-data-science)
* [Google Data Analytics Professional Certificate, ongoing](https://www.coursera.org/professional-certificates/google-data-analytics#courses)

